\SW: I. Crowd-sourcing the Discovery of Gravitational Lenses

### 2015-07-22 doc/sw-system-referee-response.txt

We thank the referee for their very helpful comments, all of which we
address below.  Their comments are shown unindented, while our
responses are shown indented.

 - - - - - - - - - - - - - - - - - - - -

This work merits publication after some minor revisions.

Following the order of the text, my comments (on both form and
content) are:

In the abstract, "expert-classified images which lack lenses" should
be replaced by something like "real images that lack lenses" or
"observed images that lack lenses", talking about "expert classified
images" when referring to non lenses seems a bit confusing.

    Done.

Page 9, 4 lines after equation (2), "Nx is the number of lenses the
volunteer has been shown" should be replaced by "Nx is the number of
training subjects of the relevant type the volunteer has been shown",
since it can refer either to lenses or non lenses.

    Done.

Page 9, I do not think it is necessary to create a specific
subsubsection 4.2.1 to present the examples, which can be presented in
the rest of the text of subsection 4.2.

    Done.

Page 10, maybe the title of subsection 4.5 : "Practicalities" should
be changed for a more specific title here.

    Done. We've gone with "Application to the CFHTLS Classifications".

Page 11, Figure 5, the figure is interesting but it should be better
highlighted with clearer color contrasts, for the histograms and for
the circles.

    TO DO! Edit SWAP to make red and blue points bigger, red and blue
    trajectories thicker and less alpha'd, red and blue histograms
    in the foregroun with alpha=1. Issued as #219

Page 12, Figure 6, the different linestyles should be replaced by
different colors to make the whole plots more readable, and to be able
to distinguish the 4 "stars" corresponding to a lens probability
threshold of 0.95 in each case. Still for this figure, in the caption,
"Lens probability varies along the curve" should be replaced by "Lens
probability threshold varies..."

     TO DO! Plot edits issued as #220.
     Caption: Done.

Page 12, in the caption of Figure 7, the authors should add a sentence
about the inset as in the caption of Figure 6 : "The inset shows a
magnified view of the bottom righthand corner of the plot".

    Done.

Page 12, subsection 5.1, paragraph 5, line 9, I would replace "If the
training set samples from the same systems as the test set" by "AS the
training set samples..."

    This was not a typo: we have clarified what we mean (using better
    grammar!) in the text as follows:

    "If the training set were to be sampled fairly from test set, the
    completeness of the training set would be equal to the completeness of
    the test set. (In practice this will likely only be approximately
    true, as simulated lenses [and the distributions of their properties]
    are used instead of real ones.)"

    We think this will make sense to the reader, as we discuss the
    efforts we made to make the training sims realistic elsewhere.

Page 15, last paragraph before Section 6, first sentence, there is a
repetition of "between".

    Fixed.

Page 16, subsection 6.1, I would write the first sentence of the 3rd
paragraph: "The false positives show similar behavior.." at the end of
the second paragraph, and begin the 3rd paragraph with "As well as
subjects being 'unlucky'...".

    Done.

Page 18, the last paragraph of subsection 6.2 quickly deals with the
subject of automated lens searches. I would have liked to read more
development on that subject, which I could find though in Space Warps
II. Nevertheless, I think the authors should at least add a sentence
or two about it in their conclusion, maybe by completing the last
indent of Section 7 concerning the missed lenses.

    We have added the following to the last conclusion bullet, to
    close this loop as the referee suggests:

    "Future searches will need to address of these issues. We expect
    it to be especially interesting to try crowd-sourcing the visual
    inspection of target systems which have had their candidate lens
    galaxy light automatically subtracted off (as, for example,
    RingFinder does), in a collaboration between humans and
    machines."

Page 18, I think the title of subsection 6.3 : "Increasing capacity"
should be changed to "Increasing crowd capacity" to avoid confusion.

    Done.

Page 18, subsection 6.3, 1st paragraph, line 7, there is a 'typo' :
"quantitively".

    Fixed.

The authors should add a discussion about the complexity of computing
of a selection function in the case of visual inspection compared to
the automated methods.

    TO DO.

### 2015-07-22 doc/sw-system.tex
Added note on RingFinder to last conclusion bullet #216

\item The simulated gravitational lenses that were missed were predominantly
galaxy-scale lenses with faint blue galaxy sources, whose lensed features are
difficult to distinguish from the light from the lens galaxy (consistent
with what we find also for real lenses, see \PaperTwo). We observed some
additional scatter, with some simulated lenses accumulating low probability
simply due to classification noise.

>>>>

\item The simulated gravitational lenses that were missed were predominantly
galaxy-scale lenses with faint blue galaxy sources, whose lensed features are
difficult to distinguish from the light from the lens galaxy (consistent
with what we find also for real lenses, see \PaperTwo). We observed some
additional scatter, with some simulated lenses accumulating low probability
simply due to classification noise. Future searches will need to address
of these issues. We expect it to be especially interesting to try
crowd-sourcing the visual inspection of target systems which have
had their candidate lens galaxy light automatically subtracted off (as, for example, \RF
does), in a collaboration between humans and machines.
